---
title: "Causal Project"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(did)
library(haven)
library(dplyr)
library(tidyverse)
library(zoo)
library(lubridate)
library(stats)
library(collapse)
library(xlsx)
library(kableExtra)
library(readxl)
```

## Describing the Data and Methodology

 

```{r, echo=FALSE, include=FALSE}
# This is the preparation file that imports the cleaned and reduced version of all the datasets, using Stata, of my data 
# ucr_meth <- read_dta("G:/Causal Inference/Data/ucr_meth.dta")
ucr_meth <- read_dta("C:/Users/gaeta/Documents/GitHub/CausalReasearch/ucr_meth.dta")

UCR <- zap_formats(ucr_meth) #
UCR<- zap_label(UCR) # Need to zap stuff because my data set does not play nice with R

# Dropping the states that were dropped
remove <- c("AL", "AK", "AZ", "AR", "CA", "CT", "DC","DE", "HI", "ME", "MA", "MS", "NH", "NJ", "NY", "OR", "PA", "RI", "VT", "WA", "WY", "KY")
UCR <- UCR[!UCR$stname %in% remove,]
UCR <- UCR[complete.cases(UCR), ] # dropping varables without a name or stateip

UCRQuarter <- UCR %>%
  mutate(Quarter = ceiling(as.numeric(UCR$month) / 3)) # Specifying which quarter the data belongs in accroding to the month

UCRTEST <- collapse::collap(UCRQuarter, ~ stname + year + Quarter) # Aggregating by the state name, the year and quarter 

# write.xlsx(UCRTEST, file = "G:/Causal Inference/Data/CleanUP1.xlsx") # Exporting the data as an excel spreadsheet so that I can mually add in the First.Treat and treat columns 
write.xlsx(UCRTEST, file = "C:/Users/gaeta/Documents/GitHub/CausalReasearch/CleanUP1.xlsx")


# Read in the modified excel spreadsheet
# CleanUP <- read_excel("G:/Causal Inference/Data/CleanUP.xlsx")
CleanUP <- read_excel("C:/Users/gaeta/Documents/GitHub/CausalReasearch/CleanUP.xlsx")

CleanUPWork <- collap(CleanUP, ~ stname + year, custom = list(fmean= 22, fmean= 1, fsum = 4:21, fsum = 23)) # Collapse data where we are taking the mean of column 1 and 22, representing state id and year, and summing the rest of the rows 

CleanUPWork$treated <- ifelse(CleanUPWork$treated>1,1,0) # need to round the treated column down to 1 if greater than 1 as we want it to be a binary.
```

For this paper, I will be using data from the FBI's Uniform Crime Reporting (UCR) Program from 1997 to 2007 that I have acquired from Justin McCrary's personal page as well as the same states used by Callaway and Sant'Anna (2020). 

The UCR collects the number of offenses that have come to the attention of law enforcement for violent and property crime, as well as data concerning clearances of these  offenses. Violent crimes are defined in the UCR Program as offenses that involve force or threat of force, thus including murder, manslaughter, rape, robbery and aggravated assaults. On the other hand, crimes such as burglary, larceny/theft, motor vehicle theft and arson are considered as property crime as there is no use of force or threat of force against the victims. 

I decided to not include aggravated assaults and arson offenses as they are either redundant, as it is the case for aggravated assaults, or there is only a limited amount of data, as is the case for arson. 
In the case for aggravated assaults, the FBI states that when "aggravated assault and larceny-theft occur together, the offense falls under the category of robbery" meaning that the crime occurred due to a financial motive that might be impacted by changes in the minimum wage, either because the victim is perceived as wealthier by the criminal or the criminal lost their source of income. 


However, one could argue that I should not incldue the rest of the violent crimes (i.e. murder, manslaughter and rape) as these are crimes with the purpose of committing harm. I argue that some of these crimes could have occurred as an escalation of non-violent crimes, thus making these violent crimes more akin to crime of opportunity. Unlike the distinction between robbery and aggravated assault, it is unclear whether police report a crime as both a rape, or any other violent crime, and robbery or if they just report the crime as the most serious offense. Either way, the inclusion of these violent crimes, regardless of their motive, does not change the results as I am looking at the effect of changes to the minimum wage on all types of crime.

In order to perform my analysis, I am using the same method as Callaway and Sant'Anna (2020) called difference-in-difference with multiple time periods rather than the regular difference-in-difference (DID) method. The reason is that a regular DID setup requires that there are two time periods and two groups: in the first period no group is treated, and in the second period one group is treated whereas the other is not. However, changes in the minimum wage have occurred in in some states at different time periods and have not occurred in others. Consequently, this means that we have a consistent group of states that are untreated, as they have not changed their minimum wage, but we have a group of states that are "treated" at different time periods, thus making a regular DID difficult to do. 

The core of their method is to separate the DID analysis into three separate steps: identification, aggregation of parameters, and estimation about these different parameters. 

  

## Performing the Analysis

### Identification

Given that there are different potential outcomes for each state that cannot be observed for the same state at the same time, we need to identify and estimate the causal effect of treatment. As we can see from the table of the group-time average treatment effects without covariates on larceny crimes that there is evidence of a positive effect of the minimum wage on larceny crimes. These results suggest that I should aggregate the group-time average treatment effect.


When I aggregate the group-time average treatment effect, the positive effect of minimum wage on larceny is still statistically significant. 

```{r}
############################## rape
attrape_pc <- att_gt(yname = "rape_pc", # LHS variable
               tname = "year", # time variable
               idname = "statefip", # id variable
               gname = "First.Treat", # first treatment period variable
               data = CleanUPWork, # data
               xformla = NULL, # no covariates
               est_method = "dr", # "dr" is doubly robust. "ipw" is inverse probability weighting. "reg" is regression
               control_group = "nevertreated", # set the comparison group which is either "nevertreated" or "notyettreated" 
               bstrap = TRUE, # if TRUE compute bootstrapped SE
               biters = 1000, # number of bootstrap iterations
               print_details = FALSE,
               clustervars = "statefip", # cluster level
               panel = TRUE) # whether the data is panel or repeated cross-sectional

# Aggregate ATT
agg_effects <- aggte(attrape_pc, type = "group")
summary(agg_effects)

# Group-time ATTs
summary(attrape_pc)

# Plot group-time ATTs
ggdid(attrape_pc)

# Event-study
agg_effects_es <- aggte(attrape_pc, type = "dynamic", na.rm = TRUE)
summary(agg_effects_es)
rape <- cbind(c(round(agg_effects_es$overall.att, digits = 3), "(-9.37, 2.67)"))
# Plot event-study coefficients
ggdid(agg_effects_es)




############################## larceny
attlarceny_pc <- att_gt(yname = "larceny_pc", # LHS variable
                  tname = "year", # time variable
                  idname = "statefip", # id variable
                  gname = "First.Treat", # first treatment period variable
                  data = CleanUPWork, # data
                  xformla = NULL, # no covariates
                  #xformla = ~ l_police, # with covariates
                  est_method = "dr", # "dr" is doubly robust. "ipw" is inverse probability weighting. "reg" is regression
                  control_group = "nevertreated", # set the comparison group which is either "nevertreated" or "notyettreated" 
                  bstrap = TRUE, # if TRUE compute bootstrapped SE
                  biters = 1000, # number of bootstrap iterations
                  print_details = FALSE,
                  clustervars = "statefip", # cluster level
                  panel = TRUE) # whether the data is panel or repeated cross-sectional

agg_effects1 <- aggte(attlarceny_pc, type = "group")
summary(agg_effects1)

# Group-time ATTs you want this 
summary(attlarceny_pc)

# Plot group-time ATTs
ggdid(attlarceny_pc)

# Event-study you want this 
agg_effects_es1 <- aggte(attlarceny_pc, type = "dynamic", na.rm = TRUE)
summary(agg_effects_es1)
larceny <- cbind(c(round(agg_effects_es1$overall.att, digits = 3), "(14.11, 227.28)*"))
# Plot event-study coefficients
ggdid(agg_effects_es1)                

# Create table of estimates, particular outcomes, row = estimated att
# table violent, table table non-violent
# what do they recommend for the group specifc att
# work in terms of _pc

############################## vehicle
attvehicle_pc <- att_gt(yname = "vehicle_pc", # LHS variable
                        tname = "year", # time variable
                        idname = "statefip", # id variable
                        gname = "First.Treat", # first treatment period variable
                        data = CleanUPWork, # data
                        xformla = NULL, # no covariates
                        #xformla = ~ l_police, # with covariates
                        est_method = "dr", # "dr" is doubly robust. "ipw" is inverse probability weighting. "reg" is regression
                        control_group = "nevertreated", # set the comparison group which is either "nevertreated" or "notyettreated" 
                        bstrap = TRUE, # if TRUE compute bootstrapped SE
                        biters = 1000, # number of bootstrap iterations
                        print_details = FALSE,
                        clustervars = "statefip", # cluster level
                        panel = TRUE) # whether the data is panel or repeated cross-sectional

agg_effects2 <- aggte(attvehicle_pc, type = "group")
summary(agg_effects2)

# Group-time ATTs you want this 
summary(attvehicle_pc)

# Plot group-time ATTs
ggdid(attvehicle_pc)

# Event-study you want this 
agg_effects_es2 <- aggte(attvehicle_pc, type = "dynamic", na.rm = TRUE)
summary(agg_effects_es2)
vehicle <- cbind(c(round(agg_effects_es2$overall.att, digits = 3), "(-165.03, 354.94)"))
# Plot event-study coefficients
ggdid(agg_effects_es2)  

############################## burglary
attburglary_pc <- att_gt(yname = "burglary_pc", # LHS variable
                        tname = "year", # time variable
                        idname = "statefip", # id variable
                        gname = "First.Treat", # first treatment period variable
                        data = CleanUPWork, # data
                        xformla = NULL, # no covariates
                        #xformla = ~ l_police, # with covariates
                        est_method = "dr", # "dr" is doubly robust. "ipw" is inverse probability weighting. "reg" is regression
                        control_group = "nevertreated", # set the comparison group which is either "nevertreated" or "notyettreated" 
                        bstrap = TRUE, # if TRUE compute bootstrapped SE
                        biters = 1000, # number of bootstrap iterations
                        print_details = FALSE,
                        clustervars = "statefip", # cluster level
                        panel = TRUE) # whether the data is panel or repeated cross-sectional

agg_effects3 <- aggte(attburglary_pc, type = "group")
summary(agg_effects3)

# Group-time ATTs you want this 
summary(attburglary_pc)

# Plot group-time ATTs
ggdid(attburglary_pc)

# Event-study you want this 
agg_effects_es3 <- aggte(attburglary_pc, type = "dynamic", na.rm = TRUE)
summary(agg_effects_es3)
burglary <- cbind(c(round(agg_effects_es3$overall.att, digits = 3), "(-37.72, 67.14)"))
# Plot event-study coefficients
ggdid(agg_effects_es3) 

############################## manslaughter
attmanslaughter_pc <- att_gt(yname = "manslaughter_pc", # LHS variable
                         tname = "year", # time variable
                         idname = "statefip", # id variable
                         gname = "First.Treat", # first treatment period variable
                         data = CleanUPWork, # data
                         xformla = NULL, # no covariates
                         #xformla = ~ l_police, # with covariates
                         est_method = "dr", # "dr" is doubly robust. "ipw" is inverse probability weighting. "reg" is regression
                         control_group = "nevertreated", # set the comparison group which is either "nevertreated" or "notyettreated" 
                         bstrap = TRUE, # if TRUE compute bootstrapped SE
                         biters = 1000, # number of bootstrap iterations
                         print_details = FALSE,
                         clustervars = "statefip", # cluster level
                         panel = TRUE) # whether the data is panel or repeated cross-sectional

agg_effects4 <- aggte(attmanslaughter_pc, type = "group")
summary(agg_effects4)

# Group-time ATTs you want this 
summary(attmanslaughter_pc)

# Plot group-time ATTs
ggdid(attmanslaughter_pc)

# Event-study you want this 
agg_effects_es4 <- aggte(attmanslaughter_pc, type = "dynamic", na.rm = TRUE)
summary(agg_effects_es4)
manslaughter <- cbind(c(round(agg_effects_es4$overall.att, digits = 3), "(-0.024, 0.076)"))
# Plot event-study coefficients
ggdid(agg_effects_es4)  

############################## robbery
attrobbery_pc <- att_gt(yname = "robbery_pc", # LHS variable
                             tname = "year", # time variable
                             idname = "statefip", # id variable
                             gname = "First.Treat", # first treatment period variable
                             data = CleanUPWork, # data
                             xformla = NULL, # no covariates
                             #xformla = ~ l_police, # with covariates
                             est_method = "dr", # "dr" is doubly robust. "ipw" is inverse probability weighting. "reg" is regression
                             control_group = "nevertreated", # set the comparison group which is either "nevertreated" or "notyettreated" 
                             bstrap = TRUE, # if TRUE compute bootstrapped SE
                             biters = 1000, # number of bootstrap iterations
                             print_details = FALSE,
                             clustervars = "statefip", # cluster level
                             panel = TRUE) # whether the data is panel or repeated cross-sectional

agg_effects5 <- aggte(attrobbery_pc, type = "group")
summary(agg_effects5)

# Group-time ATTs you want this 
summary(attrobbery_pc)

# Plot group-time ATTs
ggdid(attrobbery_pc)

# Event-study you want this 
agg_effects_es5 <- aggte(attrobbery_pc, type = "dynamic", na.rm = TRUE)
summary(agg_effects_es5)
robbery <- cbind(c(round(agg_effects_es4$overall.att, digits = 3), "(-4.37, 13.57)"))
# Plot event-study coefficients
ggdid(agg_effects_es5) 

############################## murder
attmurder_pc<- att_gt(yname = "murder_pc", # LHS variable
                        tname = "year", # time variable
                        idname = "statefip", # id variable
                        gname = "First.Treat", # first treatment period variable
                        data = CleanUPWork, # data
                        xformla = NULL, # no covariates
                        #xformla = ~ l_police, # with covariates
                        est_method = "dr", # "dr" is doubly robust. "ipw" is inverse probability weighting. "reg" is regression
                        control_group = "nevertreated", # set the comparison group which is either "nevertreated" or "notyettreated" 
                        bstrap = TRUE, # if TRUE compute bootstrapped SE
                        biters = 1000, # number of bootstrap iterations
                        print_details = FALSE,
                        clustervars = "statefip", # cluster level
                        panel = TRUE) # whether the data is panel or repeated cross-sectional

agg_effects6 <- aggte(attmurder_pc, type = "group")
summary(agg_effects6)

# Group-time ATTs you want this 
summary(attmurder_pc)

# Plot group-time ATTs
ggdid(attmurder_pc)

# Event-study you want this 
agg_effects_es6 <- aggte(attmurder_pc, type = "dynamic", na.rm = TRUE)
summary(agg_effects_es6)

murder <- cbind(c(round(agg_effects_es6$overall.att, digits = 3), "(-1.05,0.31)"))

# Plot event-study coefficients
ggdid(agg_effects_es6) 


Description <- rbind("Overall ATT", "95% CI")
Table <- cbind(Description,Murder = c(murder), Manslaughter = c(manslaughter), Rape = c(rape), Vehicle = c(vehicle), Robbery = c(robbery), Larceny = c(larceny), Burglary = c(burglary))



kbl(Table,format = "latex", caption = "Minimum Wage Aggreagted Treatment Effect Estimates", booktabs =T)%>%
add_header_above(c(" ","Violent Crimes"=3,"Non-Violent Crimes"=4))  %>%
  kable_styling(latex_options =c("striped","hold_position")) %>%
  row_spec(0:2,align = "c")
```